\subsection{Definition}
\begin{enumerate}[i.]
    \item There shall be a Society Committee who are responsible for the effective operation of the Society in pursuit of the Society’s Aims and Objectives.
\end{enumerate}

\subsection{Committee Members}
\subsubsection{President}
\begin{enumerate}
    \item Shall have overall responsibility for the society.
    \item Shall chair General Meetings of the society and meetings of the Society Committee.
    \item Shall attend Societies Council on behalf of the Society, or send a Committee Member as their deputy.
    \item Shall ensure the Society is operating in line with the Union’s compliance guidelines and processes.
    \item May be abbreviated to President, Lord President or Lady President, whichever is preferable to the incumbent.
\end{enumerate}

\subsubsection{Coordinator}
\begin{enumerate}
    \item Shall be responsible for the general administration of the Society.
    \item Shall be responsible for the organisation of meetings, including minute-taking and publicising all minutes to the Society’s membership in an appropriately timely manner.
    \item Shall be responsible for the Society’s official email address.
    \item Shall be responsible for event forms when required.
    \item Shall deputise for the President.
\end{enumerate}

\subsubsection{Treasurer}
\begin{enumerate}
    \item Shall be responsible for the financial operations of the Society.
    \item Shall aim to ensure that the Society is not running a deficit at any time.
    \item Shall be responsible for Society’s funding applications.
    \item Shall organise fundraising when necessary.
    \item Shall endeavour to organise deals or sponsorships for the Society where appropriate.
\end{enumerate}

\subsubsection{Wellbeing Secretary}
\begin{enumerate}
    \item Shall act as a point of contact to signpost Society Members to appropriate welfare services.
    \item Shall liaise with the Union to ensure that signposting information is accurate.
\end{enumerate}

\subsubsection{Social Media Secretary}
\begin{enumerate}
    \item Maintain the society’s social media presence.
    \item Promote events via communication channels.
\end{enumerate}

\subsubsection[The Tin Dog]{The Tin Dog\footnote{Reference to 28x03}}
\begin{enumerate}
    \item Shall be responsible for the maintenance of the society’s infrastructure. This includes, but is not necessarily limited to,
    \begin{enumerate}[a]
        \item Discord server(s).
        \item Website (content, domains, hosting).
        \item The page on the SU website.
    \end{enumerate}
\end{enumerate}

\subsection{Requirements}
\begin{enumerate}
    \item Committee Members must be both Society Members and Full Members of the Union.
\end{enumerate}

\subsection{Elections}
As per the Union's bylaws, Committee Members shall be elected by Single-Transferable Vote.
\begin{enumerate}[i.]
    \item All Society Members shall be eligible to vote in Society elections.
    \item All Society elections must be administered by the Union.
    \item All Society elections must be run in line with the relevant Unions governing documents.
\end{enumerate}

\subsection{Responsibilities}
All Committee Members shall
\begin{enumerate}[i.]
    \item Attend Society Committee meetings and General Meetings or submit reasonable apologies to the President.
    \item Complete relevant SU committee training, where indicated by the Union.
    \item Act in accordance with the Student Groups Code of Conduct.
\end{enumerate}

\subsection{Delegation}
The Society Committee may delegate tasks to consenting Society Members outside of the Committee, including sub-committees.
\begin{enumerate}[i.]
    \item The Society Committee must notify the Union in these instances.
    \item The Society Committee remains responsible for these tasks.
    \item Any individuals or groups delegated tasks must adhere to the Union’s governing documents including the Student Groups Code of Conduct.
\end{enumerate}

\subsection{Resignation}
A committee member may resign by giving written notice of their resignation to the President or Coordinator. The remaining committee should then organise a by-election to fill the vacant role at the discretion of the rest of the committee where appropriate.