\subsection{Definitions}
\begin{enumerate}[i.]
    \item The Society’s highest decision-making forum shall be a General Meeting.
\end{enumerate}

\subsection{Annual General Meeting}
The Society shall hold at least one General Meeting annually.
\begin{enumerate}[i.]
    \item This must be before the end of the Spring Term of each Academic Year, except at the discretion of the Activities Officer.
    \item This General Meeting must contain the following:
    \begin{enumerate}[1.]
        \item Committee Report on achievement against the Society’s Aims and Objectives.
        \item Constitution Review.
        \item Annual Financial Report and presentation of accounts.
    \end{enumerate}
\end{enumerate}

\subsection{Calling a General Meeting}
A General Meeting may be called by either:
\begin{enumerate}[i.]
    \item A simple-majority vote of the Society Committee
    \item A petition of either one third of Society Members or 20 Society Members, whichever is fewer, is presented to the Society Committee or Activities Officer.
\end{enumerate}

\subsection{Regulations}
\begin{enumerate}[i.]
    \item Notice of General Meetings must be communicated to all Society Members and the Union a minimum of 5 Union days in advance.
    \item Minutes of a General Meeting must be made available to the Society Members, via the Union website, and shared with the Union in an appropriately timely manner.
\end{enumerate}

\subsection{Attendance}
\begin{enumerate}[i.]
    \item All Society Members are entitled to speak and vote at a General Meeting.
    \item The Activities Officer is entitled to attend a General Meeting.
    \item The quorum for a General Meeting shall be either one third of Society Members or 20 Society Members, whichever is fewer.
    \begin{enumerate}[i.]
        \item If the annual General Meeting is inquorate, this shall be notified to the Activities Officer and any decisions made must be ratified by a vote of the Society Members with the same quoracy requirements.
    \end{enumerate}
\end{enumerate}